Some Nice Title Goes Here, Eventually\ldots

### 2014-08-29 doc/tacs2014/article.tex
Added stats table and clustering-references

\documentclass[10pt,conference,a4paper]{IEEEtran}
\usepackage[hidelinks]{hyperref}
\usepackage{graphicx}
\bibliographystyle{IEEEtran}
%\usepackage{

@@

\author{
	\IEEEauthorblockN{Lars Fredrik Karlstr\"om}
	\IEEEauthorblockA{Faculty of Science, Dept. of Computer Science\\ Universidad Aut\'onoma de Baja California\\ \href{mailto:fredrik.karlstrm@uabc.edu.mx}{\texttt{fredrik.karlstrm@uabc.edu.mx}}}
	\and
	\IEEEauthorblockN{Dr. Everardo Guti\'errez L\'opez}
	\IEEEauthorblockA{Faculty of Science, Dept. of Computer Science\\ Universidad Aut\'onoma de Baja California\\ \href{mailto:foo@bar.com}{\texttt{your-cool-academic-email-here@uabc.edu.mx}}}
}

@@

	\begin{abstract}
		Quick content summary.
		Motivation. (From 'Robust': High accuracy has been attained, but speedup/size improvements still important for mobile and desktop.)
	\end{abstract}
	\medskip
	\begin{IEEEkeywords}
		Intelligent character recognition, Japanese writing, \ldots
	\end{IEEEkeywords}

@@

	The Japanese writing system consists of the two \emph{kana} syllabaries \emph{hiragana} and \emph{katakana},
	as well as the sinographs commonly known as \emph{kanji} -- literally ``Han characters'' -- that stem from China.
	The Japanese Ministry of Education's official ``regular use'' (j\=oy\=o) kanji list defines a set of 2,136
	baseline characters taught in elementary-- and secondary--school education. This set is far from exhaustive, though:
	the Japanese Industrial Standard X 0208 encoding, for instance, contains 6,355 different kanji.

@@

	Should we mention alternative solutions, such as SVMs?

@@

@@

>>>>

\documentclass[10pt,conference,a4paper]{IEEEtran}
\usepackage[utf8x]{inputenc}
\usepackage[hidelinks]{hyperref}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage[T1]{fontenc}
\bibliographystyle{IEEEtran}

% This enables the kanji in the table, but all typefaces turn uglier.
% Also must be generated with xelatex
%\usepackage{xeCJK}
%\setCJKmainfont{cyberbit.ttf}

@@

\author{
	\IEEEauthorblockN{Lars Fredrik Karlstr\"om}
	\IEEEauthorblockA{Faculty of Science, Dept. of Computer Science\\ Universidad Aut\'onoma de Baja California\\ \href{mailto:fredrik.karlstrm@uabc.edu.mx}{\texttt{fredrik.karlstrm@uabc.edu.mx}}}
	\and
	\IEEEauthorblockN{Dr. Everardo Guti\'errez L\'opez}
	\IEEEauthorblockA{Faculty of Science, Dept. of Computer Science\\ Universidad Aut\'onoma de Baja California\\ \href{mailto:everardo.gutierrez@uabc.edu.mx}{\texttt{everardo.gutierrez@uabc.edu.mx}}}
}

\pgfplotsset{
	compat = newest,
	xlabel near ticks,
	ylabel near ticks
}

@@

	\begin{abstract}
		Quick content summary.
		Motivation. (From 'Robust': High accuracy has been attained, but speedup/size improvements still important for mobile and desktop.)
	\end{abstract}
	\medskip
	\begin{IEEEkeywords}
		Intelligent character recognition, artificial neural network, handwriting recognition, Japanese writing, \ldots
	\end{IEEEkeywords}

@@

	The Japanese writing system consists of the two \emph{kana} syllabaries \emph{hiragana} and \emph{katakana},
	as well as the sinographs commonly known as \emph{kanji} -- literally ``Han characters'' -- that stem from China.
	The Japanese Ministry of Education's official ``regular use'' (j\=oy\=o) kanji list defines a set of 2,136
	baseline characters taught in elementary-- and secondary--school education. \cite{hadamitzky2012japanese} This set is far from exhaustive, though:
	the Japanese Industrial Standard X 0208 encoding, for instance, contains 6,355 different kanji.

@@

	``A linear--time elastic matching algorithm for on--line recognition of handwritten Japanese characters'' (Nakagawa)
	presents the LTM--algorithm, an alternative and attractive way of extracting feature points.

	Should we mention alternative solutions, such as SVMs? Tomoe does quite a good job, for instance. Not sure if there
	are academic evaluations/references, though.

@@

	As is proven in \cite{drineas2004clustering}, this is an NP-hard problem even in the case of $k = 2$.

	Centroid-based clustering
	"Seeks to minimize the average squared distance between points in the same cluster"
	goal is to choose k centers so as to minimize $\varphi$, the total squared distance between each point and its closest center.

@@

	\subsection{Clustering}

	\ldots decided to consider the value given by the ``rule of thumb'' $k \approx \sqrt{n / 2}$ proposed in \cite{mardia2005multivariate}
	as an upper limit to the number of clusters.

	$$ k_{max} = \sqrt{6,396 / 2} \approx 57 $$

	The clusters were generated using the k--means++ algorithm,
	a variation of Lloyd's algorithm that seeks to improve the selection of the initial centroids. \cite{arthur2007k}

Total strokes: 78785

\begin{table}
	\renewcommand{\arraystretch}{1.3}
	\caption{Statistical overview of \ldots}
	\label{tbl_stroke_analysis}
	\centering
	\begin{tabular}{ c | c c c c c l }
		\hline
		  & \bfseries \% & \small $\sum$ & $\mu$ & $\sigma$ & Highest count \\ 
		\hline
		\hline
		\bfseries A & $33.20\%$ & $26,160$ & $4.09$ & $2.33$ & $15$ & \\%(蠶) \\
		\bfseries B & $1.47\%$  & $1,159$  & $0.18$ & $0.40$ & $2$  & \\%(摑) \\
		\bfseries C & $0.00\%$  & $0$      & --     & --     & --   & \\%     \\
		\bfseries D & $0.00\%$  & $0$      & --     & --     & --   & \\%     \\
		\bfseries E & $0.31\%$  & $245$    & $0.04$ & $0.19$ & $2$  & \\%(霪) \\
		\bfseries F & $12.72\%$ & $10,018$ & $1.57$ & $1.36$ & $10$ & \\%(鏐) \\
		\bfseries G & $29.98\%$ & $23,616$ & $3.69$ & $1.96$ & $13$ & \\%(鱸) \\
		\bfseries H & $22.32\%$ & $17,587$ & $2.75$ & $1.61$ & $11$ & \\%(靆) \\
		\hline
		\hline
	\end{tabular}
\end{table}

	% Statistical representation was close to perfect after the initial
	% segment of some 3k kanji
	\begin{tikzpicture}[font=\small]
		\begin{axis}[
			ybar,
			bar width=20pt,
			xlabel={Stroke feature classification},
			ylabel={Frequency (\%)},
			ymin=0,
			ymax=40,
			%ytick=\empty,
			xtick=data,
			axis x line=bottom,
			axis y line=left,
			enlarge x limits=0.2,
			symbolic x coords={A, B, C, D, E, F, G, H},
			xticklabel style={anchor=base, yshift=-\baselineskip},
			nodes near coords={\pgfmathprintnumber\pgfplotspointmeta}
		]
			\addplot[fill=white] coordinates {
				(A, 33.2)
				(B, 1.5)
				(C, 0)
				(D, 0)
				(E, 0.3)
				(F, 12.7)
				(G, 30.0)
				(H, 22.3)
			};
		\end{axis}
	\end{tikzpicture}

	\subsection{Preliminary results}

	Not done yet, but here we go.
